HPC--101 -- Cheatsheet \vspace{-2ex}

### 2019-06-25 hpc_101/cheatsheet/paper.tex
fixed typo on globus endpoint and swtiched from tmi to shm:tmi
Removed names from cheatsheet, and modified the array view to look correct compared to slurm squeue output
comment out 2ndary login node
updates and corrections

\begin{document}
\setlength{\droptitle}{-10em}
\title{HPC--101 -- Cheatsheet \vspace{-2ex}}
\date{\today}
\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\University of {\hawaii}\\Information Technology Services -- {\ci}}
\maketitle
\section{Directory Navigation}
\begin{itemize}
\item[] \texttt{cd {\pth{Directory}}}\desc{Change to directory specified}
\item[] \texttt{ls {\pth{Path}}}\desc{List the contents of the specified path}
\item[] \texttt{ls -l {\pth{Path}}}\desc{This flag list the paths content in long form}
\item[] \texttt{ls -lh {\pth{Path}}}\desc{Make the filesize humanreable}
\item[] \texttt{ls -a {\pth{Path}}}\desc{Show hidden directories and files}
%\item[] pwd \desc{Print working directory}
\end{itemize}

@@

\section{SLURM}
\subsection{Management And Monitoring}
\begin{itemize}
\item[] \texttt{sbatch \pth{slurm\_script}}\desc{Submit a slurm script to the scheduler for batch processing}
\item[] \texttt{sbatch~--array=[\#-\#]~\pth{slurm\_script}}\desc{Submit a job array to the scheduler}
\item[] \texttt{srun} \desc{Used in submitting an interactive job, or also  used within a slurm\_script}
\item[] \texttt{srun.x11} \desc{Used in submitting an interactive job, that also forwards the X, if you logged in while enabling X forwarding}
\item[] \texttt{squeue} \desc{Display all jobs running or waiting on the cluster}
\item[] \texttt{squeue -u{\lft}user{\rht}} \desc{Only display jobs for the specified user}
\item[]\texttt{sinfo} \desc{Display the partitions and nodes state}
\item[] \texttt{scancel {\lft}jobid{\rht}} \desc{Cancel the specified job}
\end{itemize}

@@

\subsection{Hosts}
\begin{itemize}
\item[] login-0001 -- \texttt{uhhpc1.its.hawaii.edu}
\item[] login-0002 -- \texttt{uhhpc2.its.hawaii.edu}
\end{itemize}

\subsection{Globus Endpoints}
\begin{itemize}
\item[] login-0001 -- \texttt{hawaii\#UHHPC1}
\item[] login-0002 -- \texttt{hawaii\#UHHPC2}
\end{itemize}

>>>>

\begin{document}
\setlength{\droptitle}{-10em}
\title{HPC--101 -- Cheatsheet \vspace{-2ex}}
\date{\today}
\author{University of {\hawaii}\\Information Technology Services -- {\ci}}
\maketitle
\section{Directory Navigation}
\begin{itemize}
\item[] \texttt{cd {\pth{Directory}}}\desc{Change to directory specified}
\item[] \texttt{ls {\pth{Path}}}\desc{List the contents of the specified path}
\item[] \texttt{ls -l {\pth{Path}}}\desc{This flag list the paths content in long form}
\item[] \texttt{ls -lh {\pth{Path}}}\desc{Make the filesize humanreable}
\item[] \texttt{ls -a {\pth{Path}}}\desc{Show hidden directories and files}
%\item[] pwd \desc{Print working directory}
\end{itemize}

@@

\section{SLURM}
\subsection{Management And Monitoring}
\begin{itemize}
\item[] \texttt{sbatch \pth{slurm\_script}}\desc{Submit a slurm script to the scheduler for batch processing}
\item[] \texttt{sbatch~--array=[\#-\#]~\pth{slurm\_script}}\desc{Submit a job array to the scheduler}
\item[] \texttt{srun} \desc{Used in submitting an interactive job, or also  used within a slurm\_script}
\item[] \texttt{squeue} \desc{Display all jobs running or waiting on the cluster}
\item[] \texttt{squeue -u{\lft}user{\rht}} \desc{Only display jobs for the specified user}
\item[]\texttt{sinfo} \desc{Display the partitions and nodes state}
\item[] \texttt{scancel {\lft}jobid{\rht}} \desc{Cancel the specified job}
\end{itemize}

@@

\subsection{Hosts}
\begin{itemize}
\item[] login node -- \texttt{uhhpc.its.hawaii.edu}
\item[] dtn 1 node -- \texttt{hpc-dtn1.its.hawaii.edu}
\item[] dtn 2 node -- \texttt{hpc-dtn2.its.hawaii.edu}

  %% \item[] login-0002 -- \texttt{uhhpc2.its.hawaii.edu}
\end{itemize}

\subsection{Globus Endpoints}
\begin{itemize}
\item[] \texttt{UH-HPC}
%% \item[] login-0002 -- \texttt{UH-HPC2}
\end{itemize}

\subsection{Downtime}
The UH-HPC has a downtime scheduled for the first Wednesday of each month
%% \item[] login-0002 -- \texttt{UH-HPC2}

\subsection{Updated Example Scripts}
Users may obtain updated example submission scripts from ``/mnt/config/examples/''

%% \item[] login-0002 -- \texttt{UH-HPC2}

\subsection{UH-HPC links}
\begin{itemize}
\item[]  \href{https://www.hawaii.edu/its/ci/xcat/}{General Information}
\item[] \href{http://go.hawaii.edu/jdG}{FAQ}
\end{itemize}
